cardinalR: Generating interesting high-dimensional data structures

### 2025-04-02 paper-cardinalR.Rmd
Updated Swiss roll p-D

To generalize the Swiss roll structure to arbitrary dimensions, we introduce a function `generate_swiss_roll(n, p, noise_sd)`, which constructs a high-dimensional version of the classic 3D Swiss roll while preserving its core characteristics.

@@

This transformation ensures a gradual decay in variance across dimensions, mimicking real-world high-dimensional structures where later dimensions often capture subtler variations. Optionally, Gaussian noise (`\mathcal{N}(0, \sigma^2)`) can be added to all dimensions using `noise_sd` to simulate measurement variability.

>>>>

To generalize the Swiss roll structure to arbitrary dimensions, we introduce a function `generate_swiss_roll(n, p)`, which constructs a high-dimensional version of the classic 3D Swiss roll while preserving its core characteristics.

@@

This transformation ensures a gradual decay in variance across dimensions, mimicking real-world high-dimensional structures where later dimensions often capture subtler variations.
